Learning Discrete Bayesian Networks from Continuous Data

### 2015-12-02 BN_discretizer_paper.tex
Add suboptimal cite

Algorithm~\ref{alg:disc_one} is guaranteed to be optimal.
For faster methods with suboptimal results, see \citet{Boulle_2006}.

@@

\begin{table}[ht]
  \centering
  \caption{
    The discretization policies for the Iris dataset with the naive Bayes structure. 
    Two methods produce same discretization policy on each continuous variable and have same prediction accuracy.
  }
\input{Table5.tex}
  \label{table:iris_table_1}
\end{table}
\end{document}
% end of file template.tex

>>>>

Algorithm~\ref{alg:disc_one} is guaranteed to be optimal.
For faster methods with suboptimal results, see \citet{Friedman_1996} and \citet{Boulle_2006}.

@@

\begin{table}[ht]
  \centering
  \caption{
    The discretization policies for the Iris dataset with the naive Bayes structure. 
    Two methods produce same discretization policy on each continuous variable and have close 10-fold prediction accuracy and log-likelihood.
  }
\input{Table5.tex}
  \label{table:iris_table_1}
\end{table}
\end{document}
% end of file template.tex
